\chapter{ML programming language}
Is a functional language, the basic notation is an expression which has a value. Each function and valuie has a type. In ml it isn't needed to declare the type. It uses an eager
evaluation: it evalueat the arguments of a function, then the function ml. The basic types are unit, bool, real, char, string and integer. A tuple is a pair of value. The unit
type isa a type that has a single value and is used for expresions that do not return a value. Bool are true, false, not number. Integer are positive and neative, the tilde 
is used to decalre a negative number. Other operation are multiplication, addition, moltiplication. 
\section{Boolean}
You cannot compare integer and real, if you compare two real number (aproximation problem) you need to write a function. Division is a function that divides real not integer.
Spectial value are NaN (not a number). ord is chatacter to integer, chr the invers operation.
\section{Conditional}
ip $<$p$>$ then $<$exp1$>$ else $<$exp2$>$ thisi is an expression so else is requierd and both part must have values.
\section{Variable}
Variable are declared in in assignemant, can change type, a function is a variable, and you can pass it as a value. To specify a type is val $<$name$>$:$<$type$>$=$<$value. A var statement changes the environment, not the statement.
\section{Functions}
A function, fn $<$parameters$>$ =$>$ n+1 is a function with parameters that has no side effects.
\section{Case statement}
Case statement are expression and exery statement needs to be exxpressed fn x=$>$ case x of $<$pattern1$>$=$>$ $<$value$>$ $|$ $<$pattern2$>$ $=>$ $<$value$>$. The default is
rapresented by the underscore.